GO enrichment

### 2021-12-20 analysis/GOenrichment.Rmd
fix tables again, finally :) haha

Let's also pull these terms out as tables

```{r}
for( i in names(results_list)) {
  print(i)
  knitr::kable(results_list[[i]] %>% filter(Eliminated == FALSE), label=i)
}

>>>>

Let's also pull these terms out as tables. `Value` is the unadjusted p-value (-3.7 = 10 * -3.7)

```{r results='asis'}
for( i in names(results_list)) {
  print(i)
  print(knitr::kable(results_list[[i]] %>% filter(Eliminated == FALSE) %>% select(TermID, Name, Value) %>% arrange(Value), caption=i))
  cat("\n")
}
